Cognate beginnings to bilingual lexical growth

### 2023-05-23 manuscript/_appendix/_model-details.qmd
Add AoA estimator

m <- add_epred_draws(nd, 
                     model_fit_4_prior,
                     ndraws = NULL, 
                     re_formula = NA) |> 
    filter(.category != "No") |> 
    pivot_wider(names_from = ".category", values_from = ".epred") |> 
    mutate(Understands = Understands + `Understands and Says`) |> 
    pivot_longer(c(Understands, `Understands and Says`),
                 names_to = ".category",
                 values_to = ".epred") |> 
    mutate(.category = factor(.category,
                              levels = c("Understands and Says",
                                         "Understands"),
                              labels = c("Production\n(Understands and Says)",
                                         "Comprehension\n(Understands)")))

m |> 
    ggplot(aes(x = age_std, y = .epred)) +
    facet_wrap(~.category) +
    stat_lineribbon(size = 0.75, 
                    colour = NA,
                    .width = c(0.95, 0.89, 0.67, 0.5)) +
    stat_summary(fun = "mean", 
                 geom = "line",
                 linewidth = 0.75) +
    scale_x_continuous(breaks = scale(seq(10, 36, 4), 
                                      mean(responses$age), 
                                      sd(responses$age))[, 1],
                       labels = seq(10, 36, 4)) +
    scale_fill_manual(values = rev(clrs), 
                      labels = c("95%", "89%", "67%", "50%")) +
    labs(x = "Age (months)", 
         y = "Probability of acquisition",
         colour = "Credible interval", 
         fill = "Credible interval") +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    theme(legend.position = "top",
          axis.ticks.x = element_line(colour = "black"),
          panel.grid = element_blank())
```

>>>>

prior_epreds <- add_epred_draws(nd, 
                                model_fit_prior,
                                ndraws = 50, 
                                re_formula = NA) |> 
    filter(.category != "No") |> 
    pivot_wider(names_from = ".category", values_from = ".epred") |> 
    mutate(Understands = Understands + `Understands and Says`) |> 
    pivot_longer(c(Understands, `Understands and Says`),
                 names_to = ".category",
                 values_to = ".epred") |> 
    mutate(.category = factor(.category,
                              levels = c("Understands",
                                         "Understands and Says"),
                              labels = c("Comprehension\n(Understands)",
                                         "Production\n(Understands and Says)")))

prior_epreds |> 
    ggplot(aes(x = age_std, y = .epred)) +
    facet_wrap(~.category) +
    geom_line(linewidth = 3/4,
              alpha = 1/2,
              aes(group = .draw),
              colour = "grey50") + 
    scale_x_continuous(breaks = scale(seq(10, 36, 4), 
                                      mean(responses$age), 
                                      sd(responses$age))[, 1],
                       labels = seq(10, 36, 4)) +
    scale_fill_manual(values = rev(clrs), 
                      labels = c("95%", "89%", "67%", "50%")) +
    labs(x = "Age (months)", 
         y = "Probability of acquisition",
         colour = "Credible interval", 
         fill = "Credible interval") +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    theme(legend.position = "top",
          axis.ticks.x = element_line(colour = "black"),
          panel.grid = element_blank())
```
